Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/eval.tex
Shortened code

Duplicating information made sense when ZIP files were stored on floppy
disks with slow seek times and high fault rates, and memory constraints
made it impossible to keep the ZIP directory in memory or the archive
was split across multiple disks.  However, care must be taken that the
metadata is consistent. For example, vulnerabilities could occur if
the length in the central directory is used to allocate memory and the
length in the local directory is used to extract without checking that
they are equal first, as was the case in the Python ZIP
library~\cite{cve-2012-7338}.

\begin{figure}[tb]
\smaller[0.5]
\input{code/zip-eod-xform}
\caption{Signatures of stream transform functions for handling the
end-to-beginning structure of ZIP files.}
\label{fig:zip-eod-xform}
\end{figure}

Figure~\ref{fig:zip-extract} shows an abbreviated version of our ZIP
file grammar.  The ZIP grammar is a good example of how transformations
capture complicated syntax in a real-world file format; existing parser
languages cannot handle a file format of this complexity.

The \cc{zip\_file} grammarfirst splits the entire file stream into two
streams based on the \cc{zip\_end\_of\_directory} transform in line 2
(whose two C function signatures are shown in
Figure~\ref{fig:zip-eod-xform}). \cc{zip\_end\_of\_directory_parse}
finds the end-of-directory header as described above, by scanning the
file backwards, and splits the file into two streams, one containing
the end-of-directory header and one containing the file contents. The
\cc{end\_of\_directory} rule is then applied to the header stream in
line 4. All offsets in the ZIP file refer to the beginning of the
file, so the stream \cc{\$file} which contains the file contents
without the header is passed as an argument to all parsers from
hereon.

>>>>

Duplicating information made sense when ZIP files were stored on floppy
disks with slow seek times and high fault rates, and memory constraints
made it impossible to keep the ZIP directory in memory or the archive
was split across multiple disks.  However, care must be taken that the
metadata is consistent. For example, vulnerabilities could occur if
the length in the central directory is used to allocate memory and the
length in the local directory is used to extract without checking that
they are equal first, as was the case in the Python ZIP
library~\cite{cve-2012-7338}.
\begin{comment}
\begin{figure}[tb]
\smaller[0.5]
\input{code/zip-eod-xform}
\caption{Signatures of stream transform functions for handling the
end-to-beginning structure of ZIP files.}
\label{fig:zip-eod-xform}
\end{figure}
\end{comment}
Figure~\ref{fig:zip-extract} shows an abbreviated version of our ZIP
file grammar.  The ZIP grammar is a good example of how transformations
capture complicated syntax in a real-world file format; existing parser
languages cannot handle a file format of this complexity.

The \cc{zip\_file} grammarfirst splits the entire file stream into two
streams based on the \cc{zip\_end\_of\_directory} transform in line 2
%(whose two C function signatures are shown in Figure~\ref{fig:zip-eod-xform}). 
\cc{zip\_end\_of\_directory_parse}
finds the end-of-directory header as described above, by scanning the
file backwards, and splits the file into two streams, one containing
the end-of-directory header and one containing the file contents. The
\cc{end\_of\_directory} rule is then applied to the header stream in
line 4. All offsets in the ZIP file refer to the beginning of the
file, so the stream \cc{\$file} which contains the file contents
without the header is passed as an argument to all parsers from
hereon.
